A Formal Model of Checked C

### 2022-12-13 sandp23/background.tex
Adding

\subsection{\checkedc Overview}
% 
\checkedc{} development began in 2015 by Microsoft Research, but it was forked
in late 2021 and is now actively managed by the Secure Software
Development Project (SSDP). Details can be found in a prior
overview~\cite{Elliott2018} or the formalism~\cite{li22checkedc}.
%

@@

\noindent
\myparagraph{Backward Compatibility}

>>>>

\subsection{\checkedc}
% 
\checkedc{} development began in 2015 by Microsoft Research, but it was forked
in late 2021 and is now actively managed by the Secure Software
Development Project (SSDP). Details can be found in a prior
overview~\cite{Elliott2018} or the formalism~\cite{li22checkedc}.
%

@@

\noindent
\myparagraph{Backward Compatibility}
\checkedc is backward compatible with legacy C in the sense that all legacy code will type-check and compile.
However, the compiler adds the aforementioned spatial safety checks to only checked pointers.
The spatial safety guarantee is partial when the code is not fully ported.
Specifically, only code that appears in \emph{checked
  code regions}, which we call \emph{checked code}, is guaranteed to be spatially safe.
Checked regions can be designated at the level of files, functions, or individual code blocks using the
\code{checked} keyword.\footnote{You can also designate~\emph{unchecked} regions  within checked ones.}
 Within checked regions, both legacy pointers and
certain unsafe idioms (\eg \emph{variadic} function calls) are disallowed.

\myparagraph{Converting C to \checkedc}
%
The safety guarantees of Checked C come with certain restrictions. For instance,
as shown below, Checked C programs cannot use address-taken variables in a
bounds expression as the bounds relations may not hold because of possible
modifications through pointers.
% 
\begin{minted}[xleftmargin=30pt, mathescape, escapeinside=||, fontsize=\footnotesize]{c}
...
array_ptr<int> p : count (n) = NULL;
|\textcolor{red}{\faTimes}|..,&n,.
\end{minted}
% 
Consequently, converting existing C programs to Checked C might require
refactoring,~\eg eliminate~\inlinecode{&n} from the program above without
changing its functionality.
% 
This might require considerable effort~\cite{duanrefactoring} depending on the
program's complexity.
% 
Recently, Machiry~\etal developed~\threec~\cite{machiry2022c} that tries to
automatically convert a program to Checked C by adding appropriate pointer
annotations.
However, as described in \threec, completely automated conversion
is \emph{infeasible}, and it requires the developer to convert some code regions
manually.
